Implementing Option Pricing Model

### 2019-12-21 draft.Rmd
Update draft.Rmd

"@ClewlowandCarverhill mention in their paper, "the control variate is a known value that is closely related to the unknown quantity to be simulated. A good control variate for an option problem might be the price of a similar type of option for which an analytic valuation equation exists. The simulation will estimate the difference between the unknown value and the control variate, and this gives a greater accuracy than the unknown value itself. The control variates are intimately related to the hedging of the option. The control Variates are not only improving efficiency but can also providing insights into the hedging of the option" (ClewlowStrickland).

@@

Those pictures are the results from the Jump world, and we could see control variates did a great job to reduce the variance of the sample. 
![This is the call payoff from the Jump world, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\Jump.png)

![This is the call payoff from Jump world with Delta-hedging, used 252 time steps, and 100 simulation.](images/DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma-hedging, used 252 time steps, and 100 simulation.](images/DeltaGammaHedgingJump.PNG)

>>>>

@ClewlowandCarverhill mention in their paper, "the control variate is a known value that is closely related to the unknown quantity to be simulated. A good control variate for an option problem might be the price of a similar type of option for which an analytic valuation equation exists. The simulation will estimate the difference between the unknown value and the control variate, and this gives a greater accuracy than the unknown value itself. The control variates are intimately related to the hedging of the option. The control Variates are not only improving efficiency but can also providing insights into the hedging of the option" (ClewlowStrickland).

@@

Those pictures are the results from the Jump world, and we could see control variates did a great job to reduce the variance of the sample. 
![This is the call payoff from the Jump world, used 252 time steps, and 100 simulations.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\Jump.png)

![This is the call payoff from Jump world with Delta-hedging, used 252 time steps, and 100 simulations.](images/DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma-hedging, used 252 time steps, and 100 simulations.](images/DeltaGammaHedgingJump.PNG)
